Title

### 2015-12-10 paper/paper.tex
add description of pipeline procedure

>>>>

To contsruct the entire pipeline, we trained a subgraph selector and subgraph
ordeer separately and combined them in the following manner:

\begin{algorithm}
\caption{Full Pipeline}
\label{pipeline_procedure}
\begin{algorithmic}
\STATE Input: $P \gets$ Full AMR representation of paragraph
\STATE Input: $selector \gets$ subgraph selector
\STATE Input: $orderer \gets$ subgraph orderer
\STATE Starting with an initial partition $p$ of $P$, perform discrete
optimization using $selector$ to find an optimal partition $p'$.
\STATE Use $orderer$ to perform a discrete optimization over potential
orderings of the subgraphs in $p'$ to find an optimal ordering $o'$.
\STATE Output the subgraphs $p'$ ordered by $o'$
\end{algorithmic}
\end{algorithm}
